AIR4Children: Artificial Intelligence and Robotics for Children

### 2021-03-03 article/tex/main.tex
#7 aligns coclusions and abstract

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
We introduce AIR4Children, Artificial Intelligence for Children, as a way to (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create affordable child-centred materials in AI and Robotics (AIR).
We present current challenges and opportunities for a child-centred approaches for AIR. 
Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, affordable and fair participation of children in areas of AIR. 
Then, we describe the avenues that AIR4Children can take with the development of open-sourced software and hardware based on our initial pilots and experiences.
Similarly, we propose to follow the philosophy of Montessori education to help children to not only develop computational thinking but also to internalise new concepts and learning skills through activities of movement and repetition.
Finally, we conclude with the opportunities of our work and mainly we pose the future work of putting in practice what is proposed here to measure the potential impact on AIR in children of different socio-economical background, developmental stages and learning abilities. 
\end{abstract}

@@

As a future work, AIR4Children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and Robotics and to evaluate the impact on these fields to children, parents and their community.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
We introduce AIR4Children, Artificial Intelligence for Children, as a way to (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create affordable child-centred materials in AI and Robotics (AIR).
We present current challenges and opportunities for a child-centred approaches for AIR. 
Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, affordable and fair participation of children in areas of AIR. 
Then, we describe the avenues that AIR4Children can take with the development of open-sourced software and hardware based on our initial pilots and experiences.
Similarly, we propose to follow the philosophy of Montessori education to help children to not only develop computational thinking but also to internalise new concepts and learning skills through activities of movement and repetition.
Finally, we conclude with the opportunities of our work and mainly we pose the future work of putting in practice what is proposed here to evaluate the potential impact on AIR to children, instructors, parents and their community. 
\end{abstract}

@@

As a future work, AIR4Children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and Robotics and to evaluate the impact on these fields to children, instructors, parents and their community.
